---
title: "Clean Raw Data"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", 
                 "glue", 
                 "googledrive", 
                 "here",
                 "janitor", 
                 "lubridate",
                 "readxl",
                 "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```

## Read in the Data from Google Drive

-   To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream .

-   you can use read_csv, readxl, etc to read in files here as if you were doing it from your local machine.

**Example below**

`chlorurus_activity <- read_csv(glue( "{dir_gdrive}/DATA_RAW/Peter Carlson/Chlorurus_Activity_data.csv")) %>%  clean_names()`

-   To add multiple files from the drive into a tibble

`multiple_files <- tibble(list.files(glue( "{dir_gdrive}/Data/Peter Carlson/"), pattern = ".csv"))`

```{r}

list_all_csv <- tibble(list.files(glue(
"{dir_gdrive}/Data/Mike Fox/fox-functional-ecology-DRYAD/data"), pattern = ".csv")) %>% 
  rename(file_name = 1)

bulk13c <- read_csv(glue(
"{dir_gdrive}/Data/Mike Fox/fox-functional-ecology-DRYAD/data/", list_all_csv$file_name[1]))

lda <- read_csv(glue(
"{dir_gdrive}/Data/Mike Fox/fox-functional-ecology-DRYAD/", list_all_csv$file_name[2]))

bootstrap <- read_csv(glue(
"{dir_gdrive}/Data/Mike Fox/fox-functional-ecology-DRYAD/", list_all_csv$file_name[3]))


aad <- read_csv(glue(
"{dir_gdrive}/Data/Mike Fox/fox-functional-ecology-DRYAD/", list_all_csv$file_name[4]))

```


## Exploring data

```{r}
colnames(bulk13c)
unique(bulk13c$Site)



```



## Explore the Data

All data is clean and published on Dryad. No need to do anything else with this script.

## Save to clean data

Because we are not modifying anything we will read the data from the same file. No need to save into clean_data folder.
